msc dissertation

### 2021-07-20 msc dissertation code.Rmd
new
newest

@@

lm1 <- lm(Discern ~ condition + veracity + veracity*condition, data = pennystudy2r1)
summary(lm1)

>>>>

#replace condition control = 0 treatment = 1
pennystudy2r1["condition"][pennystudy2r1["condition"] == 1] <- 0
pennystudy2r1["condition"][pennystudy2r1["condition"] == 2] <- 1

@@

lm1 <- lm(Discern ~ Real + Real*condition, data = pennystudy2r1)
summary(lm1)
